Supplemental Material: Multidimensional analysis and detection of informative features in human white matter

### 2021-01-25 reports/manuscript/supplemental.tex
Add nested cross-val figure. Update figures and text to remove underscores in bundle names. Add text to describe bundle profiles in supplementary material.

\preprint{NT@UW-20-21}
%\pacs{}
\begin{abstract}
In these supplemental materials we present\ldots
\end{abstract}

@@

%\newpage
\section{Online Methods}
\label{sec:methods}

@@

Data from the HBN and Cam-CAN studies were processed using the updated
Python Automated Fiber Quantification toolbox (\texttt{pyAFQ}).
\todo[inline]{Add pyAFQ citation} In addition to demonstrating the our
analysis pipeline is robust to changes in the platform and version number of
tractometry software, the use of the updated \texttt{pyAFQ} capitalized upon
the following three improvements over the legacy Matlab version
\begin{enumerate*}[%
    label=(\roman*),%
    before=\unskip{: },%
    itemjoin={{, }},%
    itemjoin*={{, and }}]
    \item the ability to ingest data provided in the BIDS format
    \cite{gorgolewski2016brain}
    \item the calculation of diffusion kertosis imaging (DKI
    \cite{jensen2005diffusion}) metrics
    \item the exclusion of the Cingulum Hippocampus bundles, which
    demonstrated low reliability in the legacy \texttt{mAFQ}.
\end{enumerate*}
We will refer to the \texttt{mAFQ} and \texttt{pyAFQ} pipeline collectively
as \texttt{AFQ}.

@@

\subsection{Sparse Group Lasso}

@@

@@

Often, the target variable $y$ is not in the domain in which the linear
model can be best fit to it. \Cref{eq:lm-approx} can be slightly
modified as:
\begin{equation}
    \hat{y} = f^{-1} \left( \mathbf{X} \hat{\beta} \right),
    \label{eq:lm-transform}
\end{equation}
where the transformation function $f^{-1}$ characterizes the transform
applied to the data before fitting the linear coefficients. For example,
For the WH, HBN, and Cam-CAN datasets, we use a logarithmic transform,
\begin{equation}
    f \left( \hat{y} \right) = \ln \left( \hat{y} \right)
    \label{eq:log-nonlinearity}
\end{equation}

@@

@@

\todo[inline]{%
    Rewrite the remainder of this section to reflect \texttt{groupyr} changes.
}

To objectively evaluate the model performance and guard against over-fitting,
we used a nested cross-validation scheme, depicted in
\cref{main:fig:methods:cross-val} for the categorical classification case.
The subjects (i.e. rows of the feature matrix $\mathbf{X}$ in
\cref{main:fig:methods:group-structure} and \cref{eq:lm}) are shuffled and
then decomposed into $k$ batches, hereafter referred to as folds. For
the ALS dataset we used $k=10$ and for the WH dataset $k=5$. For each
unique fold, we hold that fold out as the test\textsubscript{outer} set
and let the remaining data comprise the train\textsubscript{outer} set,
with the subscript indicating the depth of the nested decomposition.
We further decompose each train\textsubscript{outer} set into three
folds, and again for each unique fold, we hold out that fold as the
test\textsubscript{inner} set and let the remaining data comprise the
train\textsubscript{inner} set. At level-1 of the decomposition, we fit
an SGL model using fixed regularization meta-parameters $\alpha$
and $\lambda$, training the model using train\textsubscript{inner}
and evaluating the fit on test\textsubscript{inner}. We find
the optimal values for $\alpha$ and $\lambda$ using
hyperoptimization, implemented using the hyperopt library's \verb|fmin|
function\cite{Bergstra_2015} with a tree of Parzen estimators search
algorithm\cite{bergstra2011algorithms}. For continuous numerical $y$,
\verb|fmin| searches for meta-parameter values that minimize the median
absolute error. This can also be done minimizing the root of the mean
squared error (RMSE) or to maximizing the coefficient of determination
($R^2$). For binary categorical $y$ \verb|fmin| seeks to maximize the
classification accuracy. This can also be done maximizing the area
under the receiver operating curve (ROC AUC) or the average precision.
Using hyperoptimization, we find optimal regularization parameters and
$\hat{\beta}$ for each train\textsubscript{outer} set and then use those
to predict values for data in test\textsubscript{outer}. Thus each
subject in the dataset has a predicted phenotype derived from a model
that never saw its particular subject's data.

The above procedure describes $k$-fold cross validation. In fact, we use
repeated $k$-fold cross validation on the outer level of the decomposition, so
that the input data is decomposed into $k$ folds, three times. Thus, each
subject has three predicted phenotypes. We then take the mean predicted value to
summarize the performance of the model. In the classification case, the
shuffling into folds is stratified such that each fold has a population that
preserves the percentage of each class found in the larger input data.

@@

The full software implementation of the SGL approach presented here is available
in a Python software package called AFQ-Insight, which is developed publicly in
\url{https://github.com/richford/afq-insight}. The version of the code used to
produce the results herein is also available in
\url{https://doi.org/10.5281/zenodo.3585942}.
\todo[inline]{Update version here}
AFQ-Insight reads the target and feature data that has been processed by AFQ
from comma separated value (CSV) files conforming to the AFQ-Browser data
format \cite{yeatman2018browser} and represents them internally as
\lstinline{DataFrame} objects from the pandas Python
library \cite{mckinney2010data}. The software provides different options for
imputing missing data in the feature matrix. Missing interior nodes are imputed
using linear interpolation. For missing exterior nodes, the user may choose
between linear extrapolation and constant forward(back)-fill. Imputation uses
only values from adjacent nodes in the same white matter bundle in the same
subject so there is no danger of data leakage from other subjects. It uses the
scikit-learn \cite{scikit-learn} library to decompose input data into separate
test and train datasets, to scale each feature to have zero mean and
unit variance, and to evaluate each fit in the hyperparameter search using
appropriate classification and regression metrics such as accuracy, area
under the receiver operating curve (AUC ROC), and coefficient of determination
($R^2$). For each set of hyperparameters, we solve the SGL using a custom
proximal operator supplied to the C-OPT library\cite{copt}. Appropriate
hyperparameters are found using the hyperopt library\cite{Bergstra_2015}.

@@

Here, we present the bundle profiles and $\hat{\beta}$ coefficients
for each dataset. Throughout this section, diffusion metrics are plotted
along the length of eighteen bundles: 
right corticospinal (CST\_R),
left corticospinal (CST\_L),
right uncinate (UNC\_R),
left uncinate (UNC\_L),
left inferior fronto-occipital fasciculus (IFO\_L),
right inferior fronto-occipital fasciculus (IFO\_R),
right arcuate (ARC\_R),
left arcuate (ARC\_L),
right thalamic radiation (ATR\_R),
left thalamic radiation (ATR\_L),
right cingulum cingulate (CGC\_R),
left cingulum cingulate (CGC\_L),
callosum forceps major (FP),
callosum forceps minor (FA),
right inferior longitudinal fasciculus (ILF\_R),
left inferior longitudinal fasciculus (ILF\_L),
right superior longitudinal fasciculus (SLF\_R),
and left superior longitudinal fasciculus (SLF\_L).
We display results for two different diffusion metrics: fractional anisotropy
(fa) and mean diffusivity (md). We use lower-case letters to abbreviate the
diffusion metrics and distinguish fractional anisotropy (fa) from the
callosum forceps minor (FA).

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{sarica_coefs_profiles_fa.pdf}
    \caption{%
        {%
            \bf Fractional anisotropy (fa) bundle profiles and $\hat{\beta}$
            coefficients for ALS classification.
        }
        \label{fig:als-bp:fa}
    }
\end{figure*}

\Cref{fig:als-bp:fa,fig:als-bp:md} show the bundle profiles and regression
coefficients for the ALS dataset fa and md metrics, respectively. The scale
of the $\hat{\beta}$ axes is shared between the fa and md figures to
highlight the relative importance of the fa features over the md features.

\begin{figure*}
    \includegraphics[width=\textwidth]{sarica_coefs_profiles_md.pdf}
    \caption{%
        {%
            \bf Mean diffusivity (md) Bundle profiles and $\hat{\beta}$
            coefficients for ALS classification.
        }
        \label{fig:als-bp:md}
    }
\end{figure*}

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{wh_coefs_profiles_fa.pdf}
    \caption{%
        {%
            \bf Fractional anisotropy (fa) bundle profiles and $\hat{\beta}$
            coefficients for age regression in the WH dataset.
        }
        \label{fig:wh-bp:fa}
    }
\end{figure*}

\hspace{1em}

\begin{figure*}
    \includegraphics[width=\textwidth]{wh_coefs_profiles_md.pdf}
    \caption{%
        {%
            \bf Mean diffusivity (md) bundle profiles and $\hat{\beta}$
            coefficients for age regression in the WH dataset.
        }
        \label{fig:wh-bp:md}
    }
\end{figure*}

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{hbn_coefs_profiles_fa.pdf}
    \caption{%
        {%
            \bf Fractional anisotropy (fa) bundle profiles and $\hat{\beta}$
            coefficients for age regression in the HBN dataset.
        }
        \label{fig:hbn-bp:fa}
    }
\end{figure*}

\hspace{1em}

\begin{figure*}
    \includegraphics[width=\textwidth]{hbn_coefs_profiles_md.pdf}
    \caption{%
        {%
            \bf Mean diffusivity (md) bundle profiles and $\hat{\beta}$
            coefficients for age regression in the HBN dataset.
        }
        \label{fig:hbn-bp:md}
    }
\end{figure*}

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{cc_coefs_profiles_fa.pdf}
    \caption{%
        {%
            \bf Fractional anisotropy (fa) bundle profiles and $\hat{\beta}$
            coefficients for age regression in the Cam-CAN dataset.
        }
        \label{fig:cc-bp:fa}
    }
\end{figure*}

\begin{figure*}
    \includegraphics[width=\textwidth]{cc_coefs_profiles_md.pdf}
    \caption{%
        {%
            \bf Mean diffusivity (md) bundle profiles and $\hat{\beta}$
            coefficients for age regression in the Cam-CAN dataset.
        }
        \label{fig:cc-bp:md}
    }
\end{figure*}

>>>>

@@

%\newpage
\section{Methods}
\label{sec:methods}

@@

Data from the HBN and Cam-CAN studies were processed using the updated Python
Automated Fiber Quantification toolbox (\texttt{pyAFQ})\todo{Add pyAFQ
citation}. In addition to demonstrating the our analysis pipeline is robust
to changes in tractometry software, the use of the updated \texttt{pyAFQ}
capitalized upon the following improvements over the legacy Matlab version
\begin{enumerate*}[%
    label=(\roman*),%
    before=\unskip{: },%
    itemjoin={{, }},%
    itemjoin*={{, and }}]
    \item the ability to ingest data provided in the BIDS format
    \cite{gorgolewski2016brain}
    \item the calculation of diffusion kertosis imaging (DKI
    \cite{jensen2005diffusion}) metrics
\end{enumerate*}
We will refer to the \texttt{mAFQ} and \texttt{pyAFQ} pipeline collectively
as \texttt{AFQ}.

@@

\subsection{Sparse Group Lasso}
\label{sec:sgl}

@@

\subsubsection{Bagging meta-estimators}

\Cref{sec:sgl} describes a single SGL model. To further improve model
performance, we create ensemble models composed of $m = 20$ individual SGL
models using bootstrap aggregation (bagging) \cite{breiman1996bagging}.
Bagging relies on the underlying assumption that some of the error in a
single SGL model's prediction stems from a mismatch in the distributions of
training data used to fit the model and test data used to evaluate its
performance. To overcome this, bagging invokes the same base estimator (e.g.
SGL) many times with different training sets, which are created by sampling
the original training samples with replacement. The bagging meta-estimator's
prediction is then the average of its constituent estimators' predictions.
Likewise, when we report the hyperparameter values $\alpha$ and $\lambda$, or
regression coefficients $\hat{\beta}$, we are refering to these values
averaged over 20 estimators in the bagging meta-estimator.

@@

Often, the target variable $y$ is not in the domain in which the linear
model can be best fit to it. \Cref{eq:lm-approx} can be slightly
modified as:
\begin{equation}
    \hat{y} = f^{-1} \left( \mathbf{X} \hat{\beta} \right),
    \label{eq:lm-transform}
\end{equation}
where the transformation function $f^{-1}$ characterizes the transform
applied to the data before fitting the linear coefficients. For example,
for the WH, HBN, and Cam-CAN datasets, we use a logarithmic transform,
\begin{equation}
    f \left( \hat{y} \right) = \ln \left( \hat{y} \right)
    \label{eq:log-nonlinearity}
\end{equation}

@@

\begin{figure}[!h]
    \includegraphics[width=\columnwidth]{nested-cross-validation.pdf}
    \caption{{\bf Nested cross-validation}
        \label{fig:nested-cross-val}
        We evaluate model quality using a nested $k$-fold cross validation
        scheme. At level-0, the input data is decomposed into $k_0$ shuffled
        groups and optimal hyperparameters are found for the level-0 training
        set. To avoid overfitting, the optimal hyperparameters are themselves
        evaluated using a cross-validation scheme taking place at level-1 of
        the decomposition, where each level-0 training set is further
        decomposed into $k_1 = 3$ shuffled groups. In the classification
        case, the training and test splits are stratified by diagnosis. For
        the ALS and WH data, $k_0 = 10$, while for the HBN and Cam-CAN data,
        $k_0 = 5$.
    }
\end{figure}

@@

To objectively evaluate the model performance and guard against over-fitting,
we used a nested cross-validation scheme, which is depicted for the binary
classification case in \cref{fig:nested-cross-val}. The subjects (i.e. rows
of the feature matrix $\mathbf{X}$ in \cref{main:fig:methods:group-structure}
and \cref{eq:lm}) are first shuffled and then decomposed into $k_0$ batches,
hereafter referred to as folds. For the ALS and WH datasets, we used $k_0 =
10$ and for the HBN and Cam-CAN datasets, $k_0 = 5$. For each unique fold, we
hold that fold out as the test\textsubscript{0} set and let the remaining
data comprise the train\textsubscript{0} set, with the subscript indicating
the depth of the nested decomposition. We further decompose each
train\textsubscript{0} set into three folds, and again for each unique fold,
we hold out that fold as the test\textsubscript{1} set and let the remaining
data comprise the train\textsubscript{1} set. At level-1 of the
decomposition, we fit an SGL model using fixed regularization meta-parameters
$\alpha$ and $\lambda$, training the model using train\textsubscript{1} and
evaluating the fit on test\textsubscript{1}. We find the optimal values for
$\alpha$ and $\lambda$ using sequential model based optimization, implemented
using the scikit-optimize \verb|BayesSearchCV| class\cite{scikit-optimize}.
For continuous numerical $y$, \verb|BayesSearchCV| searches for
meta-parameter values that maximize the $R^2$ averaged over test sets. For
binary categorical $y$ \verb|BayesSearchCV| seeks to maximize the
classification accuracy. Using hyperoptimization, we find optimal
regularization parameters and $\hat{\beta}$ for each train\textsubscript{0}
set and then use those to predict values for data in test\textsubscript{0}.
Thus each subject in the dataset has a predicted phenotype derived from a
model that never saw its particular subject's data. In the classification
case, the shuffling into folds is stratified such that each fold has a
population that preserves the percentage of each class found in the larger
input data.

@@

The full software implementation of the SGL approach presented here is available
in a Python software package called AFQ-Insight, which is developed publicly in
\url{https://github.com/richford/afq-insight}. The version of the code used to
produce the results herein is also available in
\url{https://doi.org/10.5281/zenodo.3585942}\todo{Update version here}.
AFQ-Insight reads the target and feature data that has been processed by AFQ
from comma separated value (CSV) files conforming to the AFQ-Browser data
format \cite{yeatman2018browser} and represents them internally as
\lstinline{DataFrame} objects from the pandas Python library
\cite{mckinney2010data}. The software provides different options for imputing
missing data in the feature matrix. Missing interior nodes are imputed using
linear interpolation. For missing exterior nodes, the user may choose between
linear extrapolation and constant forward(back)-fill. Imputation uses only
values from adjacent nodes in the same white matter bundle in the same
subject so there is no danger of data leakage from other subjects. It uses
the scikit-learn \cite{scikit-learn} library to decompose input data into
separate test and train datasets, to scale each feature to have zero mean and
unit variance, and to evaluate each fit in the hyperparameter search using
appropriate classification and regression metrics such as accuracy, area
under the receiver operating curve (AUC ROC), and coefficient of
determination ($R^2$). For each set of hyperparameters, we solve the SGL
problem using the \texttt{groupyr} library \cite{groupyr}. Appropriate
hyperparameters are found using the scikit-optimize library
\cite{scikit-optimize}.

@@

Here, we present the bundle profiles and $\hat{\beta}$ coefficients
for each dataset. Throughout this section, diffusion metrics are plotted
along the length of eighteen bundles: 
right corticospinal (CSTR),
left corticospinal (CSTL),
right uncinate (UNCR),
left uncinate (UNCL),
left inferior fronto-occipital fasciculus (IFOL),
right inferior fronto-occipital fasciculus (IFOR),
right arcuate (ARCR),
left arcuate (ARCL),
right thalamic radiation (ATRR),
left thalamic radiation (ATRL),
right cingulum cingulate (CGCR),
left cingulum cingulate (CGCL),
callosum forceps major (CFP),
callosum forceps minor (CFA),
right inferior longitudinal fasciculus (ILFR),
left inferior longitudinal fasciculus (ILFL),
right superior longitudinal fasciculus (SLFR),
and left superior longitudinal fasciculus (SLFL).
We display results for two different diffusion metrics: fractional anisotropy
(FA) and mean diffusivity (MD), which are extracted from different diffusion
models depending on the dataset: diffusion tensor imaging (DTI) for the ALS
and WH datasets and diffusion kurtosis imaging (DKI) for the HBN and Cam-CAN
datasets \cite{jensen2005diffusion}. The diffusion metric is always plotted
on the left $y$-axis while the $\hat{\beta}$ coefficients are displayed on
the twin axis on the right-hand-side. The scale of the $\hat{\beta}$-axis is
shared between the FA and MD metrics so that one can compare the relative
imporance of each metric.

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{sarica_coefs_profiles_fa.pdf}
    \caption{%
        {%
            \bf Fractional anisotropy (FA) bundle profiles and $\hat{\beta}$
            coefficients for ALS classification.
        }
        \label{fig:als-bp:fa}
    }
\end{figure*}

\Cref{fig:als-bp:fa,fig:als-bp:md} show the bundle profiles and regression
coefficients for the ALS dataset FA and MD metrics, respectively. These
figures reinforce the findings in the main text that ALS is localized to the
corticospinal tract. In this study, SGL selected the right corticospinal
tract (CSTR) as important and regularized coefficients in the CSTL. Yet,
\cref{fig:als-bp:fa} also shows group FA differences in the CSTL. This
highlighted a potential drawback of the SGL method, discussed in the main
text in the context of age regression. Namely, SGL is not guaranteed to
identify \emph{all} important features. In this case, if the diagnostic
signal in the CSTL is redundant to that in the CSTR, SGL will regularize the
CSTL features, thereby reducing its sparsity penalty without any
corresponding increase in loss. This parsimony cuts both ways; it is a
feature of the method when one seeks an efficient predictive model, but is a
defect of the method when one wants an exhaustive explanation of feature
importance. We will use the phrase ``parsimonious pitfall'' to refer to the
case when SGL regularizes away redundant but obviously important features.

\begin{figure*}
    \includegraphics[width=\textwidth]{sarica_coefs_profiles_md.pdf}
    \caption{%
        {%
            \bf Mean diffusivity (MD) Bundle profiles and $\hat{\beta}$
            coefficients for ALS classification.
        }
        \label{fig:als-bp:md}
    }
\end{figure*}

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{wh_coefs_profiles_fa.pdf}
    \caption{%
        {%
            \bf Fractional anisotropy (FA) bundle profiles and $\hat{\beta}$
            coefficients for age regression in the WH dataset.
        }
        \label{fig:wh-bp:fa}
    }
\end{figure*}

\Cref{fig:wh-bp:fa,fig:wh-bp:md} show the bundle profiles and regression
coefficients for the WH dataset. In contrast to the ALS classification case,
the $\hat{\beta}$ coefficients are distributed widely through the brain, supporting
the interpretation that aging is a large and continuous whole-brain process.
These figures also show that SGL behaves much more like the lasso than the group
lasso, as discussed in the main text. The parsimonious pitfall is most evident in
the IFOL and IFOR bundles in \cref{fig:wh-bp:md}.

\begin{figure*}
    \includegraphics[width=\textwidth]{wh_coefs_profiles_md.pdf}
    \caption{%
        {%
            \bf Mean diffusivity (MD) bundle profiles and $\hat{\beta}$
            coefficients for age regression in the WH dataset.
        }
        \label{fig:wh-bp:md}
    }
\end{figure*}

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{hbn_coefs_profiles_fa.pdf}
    \caption{%
        {%
            \bf Fractional anisotropy (FA) bundle profiles and $\hat{\beta}$
            coefficients for age regression in the HBN dataset.
        }
        \label{fig:hbn-bp:fa}
    }
\end{figure*}

\Cref{fig:hbn-bp:fa,fig:hbn-bp:md} show the bundle profiles and regression
coefficients for the HBN dataset. Like the WH dataset, the $\hat{\beta}$
coefficients are distributed widely through the brain and SGL behaves more
like the lasso than the group lasso. In contrast the the WH results,
the bundle profiles show different behaviors. For example the SLFL and SLFR
bundle profiles in \cref{fig:wh-bp:md} and \cref{fig:hbn-bp:md} have
different concavity. This is unsurprising, however, given the differences
between these datasets 
\begin{enumerate*}[%
    label=(\roman*),%
    before=\unskip{: },%
    itemjoin={{, }},%
    itemjoin*={{, and }}]
    \item different diffusion models, with DTI for the WH dataset and DKI for
    the HBN dataset
    \item different age ranges and distributions (which is evident in the
    figure legends), with HBN being a developmental dataset, while WH is a
    lifespan maturation dataset
    \item different anatomical extents, with the WH streamlines truncated to
    remain with the bundle's bounding regions of interest (the default
    behavior in the legacy \texttt{mAFQ}) and the HBN streamlines allowed
    to retain their full extent from whole-brain tractography (the default
    behavior in \texttt{pyAFQ}).
\end{enumerate*}
Thus, one should use caution when comparing bundle profiles and $\hat{\beta}$
coefficients between the WH, HBN, and Cam-CAN models.
The parsimonious pitfall is most evident in the UNCL, UNCR, ARCL, SLFL, and
SLFR bundles in \cref{fig:hbn-bp:md}.

\begin{figure*}
    \includegraphics[width=\textwidth]{hbn_coefs_profiles_md.pdf}
    \caption{%
        {%
            \bf Mean diffusivity (MD) bundle profiles and $\hat{\beta}$
            coefficients for age regression in the HBN dataset.
        }
        \label{fig:hbn-bp:md}
    }
\end{figure*}

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{cc_coefs_profiles_fa.pdf}
    \caption{%
        {%
            \bf Fractional anisotropy (FA) bundle profiles and $\hat{\beta}$
            coefficients for age regression in the Cam-CAN dataset.
        }
        \label{fig:cc-bp:fa}
    }
\end{figure*}

\Cref{fig:cc-bp:fa,fig:cc-bp:md} show the bundle profiles and regression
coefficients for the Cam-CAN dataset. Like the WH and HBN datasets, the
$\hat{\beta}$ coefficients are distributed widely through the brain and SGL
behaves more like the lasso than the group lasso. As before, one must be
cautious about comparing bundle profiles and $\hat{\beta}$ coefficients
between models. While the HBN and Cam-CAN datasets share the same diffusion
model and refrain from clipping streamlines, the age distributions for the
two are roughly disjoint, with the WH age distribution straddling the two.
The parsimonious pitfall is again evident in the UNCL, UNCR, ARCL, SLFL, and
SLFR bundles in \cref{fig:cc-bp:md}.
\todo[inline]{We could say more here but it's not an ``aging'' paper so I
don't really want to. I only want to stress that you have to be careful
comparing $\hat{\beta}$ across models.}

\begin{figure*}
    \includegraphics[width=\textwidth]{cc_coefs_profiles_md.pdf}
    \caption{%
        {%
            \bf Mean diffusivity (MD) bundle profiles and $\hat{\beta}$
            coefficients for age regression in the Cam-CAN dataset.
        }
        \label{fig:cc-bp:md}
    }
\end{figure*}
